Adopting agile in the large: motivations, success factors and challenges

### 2014-05-06 journal/article.tex
Differing vocabularies

@@

% Differing vocabularies

>>>>

% Challenge: Differing vocabularies

In a large environment many agile teams coexist and it is possible that their
agile models and vocabularies start diverging. When many teams implement agile
without consistent guidance friction and fragmentation may be generated [P9].
The organization may require moving people between teams from time to time, and
therefore it would be desirable that no big differences in teams' agile cultures
exist. Divergence in process would create risk increasing costs when relocating
people [P38]. Further, if processes of teams diverged management had
difficulties in forecasting and comparing work of different teams [P38, P48].
To overcome problems with divergence in agile models some organizations defined
standards to follow [P8, P43].

% Coordinating between many teams

* Hard to create roadmap between teams --> Teams see only their own priorities

@@
